Proper radial distance as a coordinate in the Schwarzschild metric

### 2022-06-19 arxiv/template.tex
start conclusions

\bibliographystyle{unsrtnat}
\bibliography{references}

>>>>

We have presented physical diagrams of a spherically symmetric black
hole using proper radial coordinate $u_1$ instead of circumferential
radius $r$.  One issue is the fact that $u_1$ coordinates do not cover
the interior of the event horizon $r<1$.  This gives the various null
geodesic and light inextensible string diagrams a different appearance
in $u_1$ coordinates.

\bibliographystyle{unsrtnat}
\bibliography{../stringrefs}
